Building table-like applications using cached data

### 2014-05-04 english_version/IEEE_TKDE/paper_main.tex
added biography, acknowledgements

\author{Sergey~Mosin,
        Sergey~Zykin % <-this % stops a space
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem S. Mosin, S. Zykin are with the
Omsk Department of Sobolev Institute of Mathematics, Omsk, Russia. The paper is
supported by RFBR grant \#12-07-00066-a.\protect\\
% note need leading \protect in front of \\ to get a newline within \thanks as
% \\ is fragile and will error, could use \hfil\break instead.
E-mail: svmosin@gmail.com, szykin@mail.ru}% <-this % stops a space
\thanks{}}

@@

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
%\boldmath
We primarily address the usage of cached Database query results in our paper.
This problem was already discussed and has some software implementations. In our
work, we propose Truth spaces usage in logical formulas while querying a Database.
This approach is supposed to help an analyst, who works with dynamically built
data representations logically described as multidimensional tables. Those
representations don't take much disk space, so one can use GPU to speed up the
computations. We consider queries in a form of relational algebra expressions,
similar to "universal relational query". Logical formulas in the queries are
presented in Disjunctive Normal Form. They consist of atomic expressions
consisting of SQL predicates. In the paper we consider single and multiple table
cases to build new data representations.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway. In particular, the Computer Society does
% not want either math or citations to appear in the abstract.

@@

@@

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{Sergey Mosin}
is a PhD student in an Omsk Department of Sobolev Institute of Mathematics. His
research interests include Databases, Data analysis, Algorithm Theory and
Internet technologies. Mosin received a Specialist degree in Applied Mathematics
and Computer Science from Omsk F. M. Dostoevsky State University. Contact him at
svmosin@gmail.com
\end{IEEEbiographynophoto}

@@

\begin{IEEEbiographynophoto}{Sergey Zykin}
Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.
\end{IEEEbiographynophoto}

>>>>

\author{Sergey~Mosin,
        Sergey~Zykin % <-this % stops a space
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem S. Mosin, S. Zykin are with the
the Siberian Branch of the Russian Academy of Sciences, Omsk, Russia.\protect\\
% note need leading \protect in front of \\ to get a newline within \thanks as
% \\ is fragile and will error, could use \hfil\break instead.
E-mail: svmosin@gmail.com, szykin@mail.ru}% <-this % stops a space
\thanks{}}

@@

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
%\boldmath
We primarily address the usage of cached Database query results in our paper.
This problem was already discussed and has some software implementations. In our
work, we propose Truth spaces usage in logical formulas while querying a Database.
This approach is supposed to help an analyst, who works with dynamically built
data representations logically described as multidimensional tables. We consider
queries in a form of relational algebra expressions, similar to "universal
relational query". Logical formulas in the queries are
presented in Disjunctive Normal Form. They consist of atomic expressions
consisting of SQL predicates. In the paper we consider single and multiple table
cases to build new data representations.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway. In particular, the Computer Society does
% not want either math or citations to appear in the abstract.

@@

% use section* for acknowledgement
\ifCLASSOPTIONcompsoc
  % The Computer Society usually uses the plural form
  \section*{Acknowledgments}
\else
  % regular IEEE prefers the singular form
  \section*{Acknowledgment}
\fi

The authors would like to thank the Russian Foundation for Basic Research for the
grant \#12-07-00066-a.

@@

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{Sergey Vladimirovich Mosin}
is a PhD student in an Omsk Department of Sobolev Institute of Mathematics. His
research interests include Databases, Data analysis, Algorithm Theory and
Internet technologies. Mosin received a Specialist degree in Applied Mathematics
and Computer Science from Omsk F. M. Dostoevsky State University. Contact him at
svmosin@gmail.com
\end{IEEEbiographynophoto}

@@

\begin{IEEEbiographynophoto}{Sergey Vladimirovich Zykin}
is a professor, doctor of science (informatics) with a focus on theory of
databases designing and head of the laboratory at the Sobolev Institute of
Mathematics of the Siberian Branch of the Russian Academy of Sciences. He has
published some 70 scientific papers as conference-, journal-, and book
contributions. Contact him at szykin@mail.ru
\end{IEEEbiographynophoto}
